### 2014-05-21 intro.tex
Tweaks to intro

\begin{figure}
\caption{The Internet's four-layer stack model}
\label{f:stack}
\begin{centering}
\includegraphics{layers.pdf}

@@

Over the last 25 years, the Internet has transformed from an academic
networking experiment into a global utility with billions of
users. With this rise, every layer of the Internet
``stack'' has seen dramatic change.

At the \textbf{link} layer, technologies that did not exist 25 years
ago now dominate---including wireless local-area networks (Wi-Fi),
cellular networks, datacenter interconnects, and transoceanic links
with high delay.

One layer up, at the \textbf{Internet} layer, mobility is now
ubiquitous. User devices regularly change their interface IP addresses
as they roam from network to network.

At the top layer of the Internet stack---the \textbf{application}
layer---none of the dominant applications of today existed 25 years
ago, including the World Wide Web and its short flows,
progressive-download video applications (e.g., YouTube and Netflix),
and real-time streaming video (e.g., Skype and Facetime).

The whole Internet has had to grapple with this continuous
evolution. How should the protocols of the \textbf{transport} layer,
sitting in the middle of the stack between the application and the
Internet, adapt to evolving application demands above them and
evolving networks below?

One legitimate answer is that these transport-layer protocols won't be
asked to adapt at all. If the network or applications evolve, our
current protocols will either be acceptable or not when run on the new
network or in service of the new application. If a protocol works
adequately, all is well. If not, we can simply stop using the protocol
and design a fresh one that matches the new circumstances.

This approach may sound wasteful, but it describes the extraordinarily
successful path taken over the last 25 years. Looking at just one
function of the transport layer---congestion control, the job of
dividing up the network's resources among contending
users---researchers have accommodated new applications and network
behaviors by devoting considerable effort to develop newer and newer
mechanisms, at least 40 in total so far (Figure \ref{f:march}).

@@

For contemporary mechanisms (e.g., TCP Cubic, the current default in
Linux), it's difficult to state the assumptions that the transport
makes about lower layers and to predict when those assumptions would
no longer hold. This presents a challenge for link-layer designers who
wish to design a new networking technology. Because of Cubic's
popularity, it can be a \emph{de facto} requirement that Cubic perform
well over any new network. In effect, this means that the designer of
the new link layer must try to satisfy Cubic's implicit assumptions in
order to achieve adequate performance.

This has led to the ``bufferbloat''\cite{bufferbloat} problem, which
comes from a link layer's attempt to hide losses from the transport,
on the grounds that the transport will assume that losses are a signal
to slow down. It has also led to a lack of parallelism in Internet
routing---flows only take one path, even if speedups might be
available by splitting flows across multiple routes---on the grounds
that the transport protocol probably assumes that out-of-order packets
are a pathology.

On the flip side, it is nontrivial to adjust the assumptions made by
the transport layer. There's no clear way to tweak the assumptions and
then retrace the same design process that was followed by a protocol's
designers, in order to explore the mechanism they would have produced
given a different starting point.

>>>>

\begin{figure}
\caption{The Internet's four-layer model}
\label{f:stack}
\begin{centering}
\includegraphics{layers.pdf}

@@

Over the last 25 years, the Internet has transformed from an academic
networking experiment into a global utility with billions of
users. As part of this transformation, every layer of the Internet
``stack'' has seen dramatic change.

At the link layer, technologies that did not exist 25 years
ago now dominate---including wireless local-area networks (Wi-Fi),
cellular networks, datacenter interconnects, and transoceanic links
with high delay.

One layer up, at the Internet layer, mobility is now
ubiquitous. User devices regularly change their interface IP addresses
as they roam from network to network.

At the top layer of the Internet stack---the application
layer---none of the dominant applications of today existed 25 years
ago, including the World Wide Web and its short-length flows,
progressive-download video applications (e.g., YouTube and Netflix),
and real-time streaming video (e.g., Skype and Facetime).

All of the Internet has had to grapple with this continuous
evolution. How should the protocols of the transport layer,
sitting in the middle of the stack between the application and the
Internet, adapt to changing applications above them and
evolving networks below?

One legitimate answer may be that transport-layer protocols need not
adapt. If the network or applications evolve, and a transport
protocol no longer works adequately alongside then, we can simply stop
using the protocol and design a fresh one that matches the new
circumstances.

This approach broadly characterizes the Internet's extraordinarily
successful path over the last 25 years. Looking at just one
function of the transport layer---congestion control, the job of
dividing up the network's resources among contending
users---researchers have accommodated new applications and network
behaviors by devoting considerable effort to develop new
mechanisms, at least 40 in total so far (Figure \ref{f:march}).

@@

For contemporary mechanisms (e.g., TCP Cubic, the current default in
Linux), it's difficult to state the assumptions that the transport
makes about lower layers and to predict when those assumptions would
no longer hold. This presents a challenge for link-layer designers who
wish to design a new networking technology. Because of Cubic's
popularity, it has become a \emph{de facto} requirement that Cubic perform
well over any new network. In effect, this means that the designer of
the new link layer must try to satisfy Cubic's implicit assumptions in
order to achieve adequate performance.

This has led to the ``bufferbloat''\cite{bufferbloat} problem:
believing that the transport layer will interpret losses as a
signal to slow down, the link layer tries to drop packets as
rarely as possible. It has also led to a lack of parallelism in
Internet routing---flows only take one path, even if speedups might be
available by splitting flows across multiple routes---on the grounds
that the transport protocol might interpret out-of-order packets
as a pathology.

On the flip side, it is usually impossible to adjust the transport
layer's assumptions in order to accommodate a new kind of
link. There's no way to tweak the assumptions and then retrace the
same design process that the protocol's designers followed, to find the
mechanism they would have produced given a different starting point.

### 2014-05-21 sprout_sprout.tex
Lowercase section headings
Small fixes
Fix figure
Tweaks to intro

\section{The Sprout Algorithm}
\label{s:sprout}

@@

Another distinguishing feature of cellular links is that users are
rarely subject to standing queues accumulated by other users, because
a cellular carrier generally provisions a separate uplink and downlink
queue for each device in a cell. In a network where two independent
users share access to a queue feeding into a bottleneck link, one user
can inflict delays on another. No end-to-end protocol can provide
low-delay service when a network queue is already full of somebody
else's packets. But when queueing delays are largely self-inflicted,
an end-to-end approach may be possible.\footnote{An end-to-end
  approach may also be feasible if all sources run the same protocol,
  but we do not investigate that hypothesis here.}

@@

\noindent \def\svgwidth{\columnwidth}\large\input{sprout-model.pdf_tex}

@@

\subsection{Evolution of the probability distribution on $\lambda$}

>>>>

\section{The Sprout algorithm}
\label{s:sprout}

@@

Another distinguishing feature of cellular links is that users are
rarely subject to standing queues accumulated by other users, because
a cellular carrier generally provisions a separate uplink and downlink
queue for each device in a cell. In a network where two independent
users share access to a queue feeding into a bottleneck link, one user
can inflict delays on another. No end-to-end protocol can provide
low-delay service when a network queue is already full of somebody
else's packets. But when queueing delays are largely self-inflicted,
an end-to-end approach may be possible.

@@

\noindent \def\svgwidth{\columnwidth}\input{sprout-model.pdf_tex}

@@

\subsection{Evolution of the belief state}
